Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints\thanks{This research was supported by the Russian Science Foundation, project No. 16-11-10150.}

### 2020-03-16 2019/NUMTA_Barkalov/SoftComputing/article.tex
Aswers for reviewer

\smartqed  % flush right qed marks, e.g. at end of proof
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{hyperref,amsmath}
\usepackage[pagewise]{lineno}
\usepackage{multirow}
\usepackage[round]{natbib} 
\usepackage[misc]{ifsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

	\textbf{Proof}. Let us consider two possible cases of the values of the indices $\nu(x_{i-1})$ and $\nu(x_i)$. 
\begin{enumerate} 
  \item If $\nu(x_{i-1}) \neq \nu(x_i)$, then according to  formulae (\ref{R_2}), (\ref{R_3}) 
\begin{equation}\label{R_glob_1}
	R(i)=R_{glob}(i)=R_{loc}(i)=2\Delta_i>0. 
\end{equation}
  \item If $\nu(x_{i-1}) = \nu(x_i) = M$, then, taking into account (\ref{current_lower_bounds}), the following inequality will hold
$$
	z_i+z_{i-1}-2z_M^* = |z_i-z_{i-1}|\leq \mu_M\Delta_i .
$$
\end{enumerate} 
From here, it will follow that for any value $r_M>1$ the following inequalities will hold
\begin{align}
	R(i) & = \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{z_i+z_{i-1}-2z_M^*}{r_M\mu_M} \geq \nonumber \\
	& \geq  \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{\mu_M\Delta_i}{r_M\mu_M} \geq \nonumber \\
  & \geq \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{\Delta_i}{r_M} = \nonumber \\
	& = \Delta_i + \Delta_i\frac{(z_i-z_{i-1})^2/\Delta_i^2}{r_M^2\mu_M^2\Delta_i^2} - 2\frac{\Delta_i}{r_M} \geq \nonumber \\
	& \geq \Delta_i + \frac{\Delta_i}{r_M^2} - 2\frac{\Delta_i}{r_M} = \Delta_i \left( 1-\frac{1}{r_M} \right)^2>0.
\end{align}
And because $r_{M}^{glob} > r_{M}^{loc} > 1$, then
\begin{align}\label{R_glob_greater_R_loc}
	R_{glob}(i) & = \Delta_i\left(1-\frac{1}{r_M^{glob}} \right)^2 > \nonumber \\
	& > \Delta_i\left(1-\frac{1}{r_M^{loc}} \right)^2 = R_{loc}(i).
\end{align}
The statement is proved.

@@

	Then, the characteristic $R_{glob}(j)$ of the interval \break
$[x_{j-1}, x_j]$, $j=j(k)$ will be strictly positive, i.e. \break
$R_{glob}(j)>0$. Indeed, at $\nu=\nu(x_j)=\nu(x_{j-1})$ and the value $r_{\nu}=r_{\nu}^{glob}$
\small
\begin{align*}
	& R(j) = \Delta_i + \frac{(z_j-z_{j-1})^2}{r_{\nu}^2\mu_{\nu}^2\Delta_i} - 2\frac{z_j+z_{j-1}-2z_{\nu}^{\ast}}{r_{\nu}\mu_{\nu}} \geq \Delta_i + \\ 
	& + 4\frac{z_{\nu}^*-\left( g_{\nu}\left( y(\bar x) \right)+L_{\nu}\sqrt{N+3}\left( (x_j-\bar x)^{\frac{1}{N}}+(\bar x - x_{j-1})^{\frac{1}{N}} \right)\right)}{r_{\nu}\mu_{\nu}}\\
	& = \Delta_i-4\frac{L_{\nu}\sqrt{N+3}\left( (x_j-\bar x)^{\frac{1}{N}}+(\bar x - x_{j-1})^{\frac{1}{N}} \right)}{r_{\nu}\mu_{\nu}} + \\
	& + 4\frac{z_{\nu}^\ast-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \geq \\
	& \geq \Delta_i\left(1-4\frac{L_{\nu}\sqrt{N+3}\max_{0\leq\alpha\leq1} {\left( \alpha^{\frac{1}{N}}+(1-\alpha)^{\frac{1}{N}} \right)}}{r_{\nu}\mu_{\nu}} \right) + \\
	& + 4\frac{z_{\nu}^{\ast}-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} = \\
	& = \Delta_i\left(1-4\frac{2^{3-1/N}L_{\nu}\sqrt{N+3}}{r_{\nu}\mu_{\nu}} \right)+4\frac{z_{\nu}^{\ast}-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} > 0.
\end{align*}
\normalsize
At $\nu=\nu(x_j ) > \nu(x_{j-1})$ and the value $r_{\nu}=r_{\nu}^{glob}$
\begin{align*}
	& R(j) = 2\Delta_i - 4\frac{z_j-z_{\nu}^{\ast}}{r_{\nu}\mu_{\nu}} \geq \\
	& \geq 2\Delta_i+4\frac{z_{\nu}^{\ast}-\left( g_{\nu}\left(y(\bar x)\right)+2L_{\nu}\sqrt{N+3}(x_j-\bar x)^{\frac{1}{N}} \right)}{r_{\nu}\mu_{\nu}} = \\
	& = 2\Delta_i - 8\frac{L_{\nu}\sqrt{N+3}(x_j-\bar x)^{\frac{1}{N}}}{r_{\nu}\mu_{\nu}}+4\frac{z_{\nu}^{\ast}-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \geq \\
	& \geq 2\Delta_i\left( 1-4\frac{L_{\nu}\sqrt{N+3}}{r_{\nu}\mu_{\nu}} \right) + 4\frac{z_{\nu}^{\ast}-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} > 0.
\end{align*}

@@

	Since we have assumed that $x'$ is a limit point for the IA-DL and  $x' \neq \bar x$, then there exists such a sequence of the intervals $[x_{t-1}, x_t], t=t(k)$ that $x' \in [x_{t-1}, x_t], R_{loc}(t)>0$, and $R_{loc}(t) \rightarrow 0$. This property of the characteristics of the intervals shrinking to the limit point has been established when proving the theorem on the convergence of the IA in \cite{Strongin2000}.

	Therefore, for large enough $k$, the following inequality will be true
\begin{equation}
	R_{glob}(j) > \rho R_{loc}(t)
\end{equation}
and (according to Rules 5 and 6 of the IA-DL method) the next iteration falls into the interval $[x_{j-1}, x_j]$, which contradicts our assumption regarding the non-limit nature of the point $\bar x$. The theorem is proven.

>>>>

\smartqed  % flush right qed marks, e.g. at end of proof
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{hyperref,amsmath}
\usepackage[pagewise]{lineno}
\usepackage{multirow}
\usepackage[round]{natbib} 
\usepackage[misc]{ifsym}
\usepackage{xcolor}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

	\textbf{Proof}. Let us consider two possible cases of the values of the indices $\nu(x_{i-1})$ and $\nu(x_i)$.

  1. If $\nu(x_{i-1}) \neq \nu(x_i)$, then according to  formulae (\ref{R_2}), (\ref{R_3}) 
\begin{equation}\label{R_glob_1}
	R(i)=R_{glob}(i)=R_{loc}(i)=2\Delta_i>0. 
\end{equation}

{ \color{red}
	2. If $\nu(x_{i-1}) = \nu(x_i) = M$, then, taking into account (\ref{current_lower_bounds}), the following inequality will be valid
$$
	z_i+z_{i-1}-2z_M^* = |z_i-z_{i-1}| = \mu \Delta_i \leq \mu_M\Delta_i,
$$
where $\mu = |z_i-z_{i-1}|/\Delta_i$.

From here, it will follow that for any value $r_M>1$ the following inequalities will hold
\begin{align}
	R(i) & = \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{z_i+z_{i-1}-2z_M^*}{r_M\mu_M} = \nonumber \\
	& = \Delta_i + \frac{\mu^2\Delta_i}{r_M^2\mu_M^2} - 2\frac{\mu\Delta_i}{r_M\mu_M} = \nonumber \\
  & = \Delta_i\left(1 + \left(\frac{\mu}{r_M\mu_M}\right)^2 - 2\frac{\mu}{r_M\mu_M}\right) = \nonumber \\
	& = \Delta_i\left(1 - \frac{\mu}{r_M\mu_M}\right)^2 \geq  \Delta_i \left( 1-\frac{1}{r_M}\right)^2 > 0.
\end{align}

And because $r_{M}^{glob} > r_{M}^{loc} > 1$ and $\mu \leq \mu_M$, then
\begin{align}\label{R_glob_greater_R_loc}
	R_{glob}(i) &= \Delta_i\left(1-\frac{\mu}{r_M^{glob}\mu_M} \right)^2 > \nonumber \\
							&> \Delta_i\left(1-\frac{\mu}{r_M^{loc}\mu_M} \right)^2 = R_{loc}(i).
\end{align}

}	
%\begin{enumerate} 
  %\item If $\nu(x_{i-1}) \neq \nu(x_i)$, then according to  formulae (\ref{R_2}), (\ref{R_3}) 
%\begin{equation}\label{R_glob_1}
	%R(i)=R_{glob}(i)=R_{loc}(i)=2\Delta_i>0. 
%\end{equation}
  %\item If $\nu(x_{i-1}) = \nu(x_i) = M$, then, taking into account (\ref{current_lower_bounds}), the following inequality will hold
%$$
	%z_i+z_{i-1}-2z_M^* = |z_i-z_{i-1}|\leq \mu_M\Delta_i .
%$$
%\end{enumerate} 
%From here, it will follow that for any value $r_M>1$ the following inequalities will hold
%\begin{align}
	%R(i) & = \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{z_i+z_{i-1}-2z_M^*}{r_M\mu_M} \geq \nonumber \\
	%& \geq  \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{\mu_M\Delta_i}{r_M\mu_M} \geq \nonumber \\
  %& \geq \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{\Delta_i}{r_M} = \nonumber \\
	%& = \Delta_i + \Delta_i\frac{(z_i-z_{i-1})^2/\Delta_i^2}{r_M^2\mu_M^2\Delta_i^2} - 2\frac{\Delta_i}{r_M} \geq \nonumber \\
	%& \geq \Delta_i + \frac{\Delta_i}{r_M^2} - 2\frac{\Delta_i}{r_M} = \Delta_i \left( 1-\frac{1}{r_M} \right)^2>0.
%\end{align}
%And because $r_{M}^{glob} > r_{M}^{loc} > 1$, then
%\begin{align}\label{R_glob_greater_R_loc}
	%R_{glob}(i) & = \Delta_i\left(1-\frac{1}{r_M^{glob}} \right)^2 > \nonumber \\
	%& > \Delta_i\left(1-\frac{1}{r_M^{loc}} \right)^2 = R_{loc}(i).
%\end{align}

The statement is proved.

@@

	Then, the characteristic $R_{glob}(j)$ of the interval \break
$[x_{j-1}, x_j]$, $j=j(k)$ will be strictly positive, i.e. \break
$R_{glob}(j)>0$. Indeed, at $\nu=\nu(x_j)=\nu(x_{j-1})$ and the value $r_{\nu}=r_{\nu}^{glob}$
\small
\begin{align*}
	& R(j) = \Delta_i + \frac{(z_j-z_{j-1})^2}{r_{\nu}^2\mu_{\nu}^2\Delta_i} - 2\frac{z_j+z_{j-1}-2z_{\nu}^{\ast}}{r_{\nu}\mu_{\nu}} \geq \Delta_i + \\ 
	& + 4\frac{z_{\nu}^*-\left( g_{\nu}\left( y(\bar x) \right)+L_{\nu}\sqrt{N+3}\left( (x_j-\bar x)^{\frac{1}{N}}+(\bar x - x_{j-1})^{\frac{1}{N}} \right)\right)}{r_{\nu}\mu_{\nu}}\\
	& = \Delta_i-4\frac{L_{\nu}\sqrt{N+3}\left( (x_j-\bar x)^{\frac{1}{N}}+(\bar x - x_{j-1})^{\frac{1}{N}} \right)}{r_{\nu}\mu_{\nu}} + \\
	& + 4\frac{z_{\nu}^\ast-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \geq \\
	& \geq \Delta_i\left(1-4\frac{L_{\nu}\sqrt{N+3}\max_{0\leq\alpha\leq1} {\left( \alpha^{\frac{1}{N}}+(1-\alpha)^{\frac{1}{N}} \right)}}{r_{\nu}\mu_{\nu}} \right) + \\
	& + 4\frac{z_{\nu}^{\ast}-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} = \\
	& = { \color{red} \Delta_i\left(1-\frac{2^{3-1/N}L_{\nu}\sqrt{N+3}}{r_{\nu}\mu_{\nu}} \right)+4\frac{z_{\nu}^{\ast}-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} } > 0.
\end{align*}
\normalsize
At $\nu=\nu(x_j ) > \nu(x_{j-1})$ and the value $r_{\nu}=r_{\nu}^{glob}$
\begin{align*}
	& R(j) = 2\Delta_i - 4\frac{z_j-z_{\nu}^{\ast}}{r_{\nu}\mu_{\nu}} \geq \\
	& \geq 2\Delta_i+4\frac{z_{\nu}^{\ast}-\left( g_{\nu}\left(y(\bar x)\right)+2L_{\nu}\sqrt{N+3}(x_j-\bar x)^{\frac{1}{N}} \right)}{r_{\nu}\mu_{\nu}} = \\
	& = 2\Delta_i - 8\frac{L_{\nu}\sqrt{N+3}(x_j-\bar x)^{\frac{1}{N}}}{r_{\nu}\mu_{\nu}}+4\frac{z_{\nu}^{\ast}-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \geq \\
	& \geq 2\Delta_i\left( 1-4\frac{L_{\nu}\sqrt{N+3}}{r_{\nu}\mu_{\nu}} \right) + 4\frac{z_{\nu}^{\ast}-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} > 0.
\end{align*}

@@

	%	Since we have assumed that $x'$ is a limit point for the IA-DL and  $x' \neq \bar x$, then there exists such a sequence of the intervals $[x_{t-1}, x_t], t=t(k)$ that $x' \in [x_{t-1}, x_t], R_{loc}(t)>0$, and $R_{loc}(t) \rightarrow 0$. This property of the characteristics of the intervals shrinking to the limit point has been established when proving the theorem on the convergence of the IA in \cite{Strongin2000}.

{ \color{red}	
	At the beginning of the proof of the theorem we have assumed that $x'$ is a limit point for the IA-DL and  $x' \neq \bar x$. This assumption implies that in the method IA-DL in the formula (\ref{R_max}) for computing the characteristic, the second component takes the highest values, i.e. $R_{glob}(t) < \rho R_{loc}(t)$. This fact corresponds to using the original index algorithm (IA) with parameters $r_\nu = r_\nu^{loc}>1, \; 1 \leq \nu \leq m+1$.

In \cite{Strongin2000} it has been proven that for any limit point $x'$ of the sequence $\{x^k\}$, generated by IA while solving the problem at any $r_\nu > 1, \; 1 \leq \nu \leq m+1$, there exists a sequence
of the intervals $[x_{t-1}, x_t], \; t=t(k)$, contracting to the point $x'$, i.e. $x' \in [x_{t-1}, x_t], \; t=t(k)$. Characteristics $R(t)$ of the intervals of the specified sequence will be positive and $R(t) \rightarrow 0$ at $k \rightarrow \infty$. 
}

	Therefore, for large enough $k$, the following inequality will be true
\begin{equation}
	R_{glob}(j) > \rho R_{loc}(t).
\end{equation}
{\color{red}

Indeed, both $j$ and $t$ depend from $k$, as the numbering of the trial points (by the lower index) changes at every iteration and the numbering of the intervals changes respectively.
However, number $j(k)$ corresponds to the same interval with fixed characteristic \linebreak $R_{glob}(j(k))>0$, whereas number $t(k)$ corresponds to different intervals with different characteristics \linebreak $R_{loc}(t(k))>0$, where $R_{loc}(t(k)) \rightarrow 0$. From this we can conclude that the condition $R_{glob}(j) > \rho R_{loc}(t)$ is fulfilled for a large enough value of $k$.
}

Hence, according to Rules 5 and 6 of the IA-DL method the next iteration falls into the interval $[x_{j-1}, x_j]$, which contradicts our assumption regarding the non-limit nature of the point $\bar x$. The theorem is proven.
